Proving linearizability using forward simulations\thanks{An extended version of this paper including the missing proofs can be found at \cite{extended}.}

### 2017-05-05 draftCAV/queue.tex
Updated queue simulation figures.
Figure placement.

The classical abstract queue implementation, denoted $AbsQ_0$, maintains a
sequence of enqueued values; dequeues return the oldest non-dequeued value, at
the time of their linearization points, or {\tt EMPTY}. Some implementations,
like the queue of \citet{journals/toplas/HerlihyW90}, denoted {\sc hwq}, are not
forward-simulated by $AbsQ_0$, even though they refine $AbsQ_0$, since the order
in which their enqueues are linearized to form $AbsQ_0$’s sequence is not
determined until later, when their values are dequeued.

@@

    \includegraphics[width=7cm]{fig-queue12}
    \caption{Forward simulation with $AbsQ$. Lines depict operations,
    and circles depict call, return, and linearization point actions.}
    \label{fig:queueSim}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.4\linewidth}
    \begin{lstlisting}
function present: $\mathbb{O} \to \mathbb{B}$
function pending: $\mathbb{O} \to \mathbb{B}$
function arg: $\mathbb{V} \to \mathbb{O}$
function before: $\mathbb{O} \times \mathbb{O} \to \mathbb{B}$

>>>>

The classical abstract queue implementation, denoted $AbsQ_0$, maintains a
sequence of enqueued values; dequeues return the oldest non-dequeued value, at
the time of their linearization points, or {\tt EMPTY}. Some implementations,
like the queue of \citet{journals/toplas/HerlihyW90}, denoted {\sc hwq} and
listed in Figure~\ref{fig:HerlihyWing}, are not forward-simulated by $AbsQ_0$,
even though they refine $AbsQ_0$, since the order in which their enqueues are
linearized to form $AbsQ_0$’s sequence is not determined until later, when their
values are dequeued.

@@

    \includegraphics[width=7cm]{fig-queue1}
    \includegraphics[width=7cm]{fig-queue2}
    \caption{Forward simulation with $AbsQ$. Lines depict operations,
    and circles depict call, return, and linearization point actions.}
    \label{fig:queueSim}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.4\linewidth}
    \begin{lstlisting}
function present: $\mathbb{O} \to \mathbb{B}$
function pending: $\mathbb{O} \to \mathbb{B}$
function arg: $\mathbb{V} \to \mathbb{O}$
function before: $\mathbb{O} \times \mathbb{O} \to \mathbb{B}$
